Predicting detection probabilities for rare and undersampled North American landbirds

### 2024-08-06 article/article.tex
update article latex code for thesis template

\documentclass[12pt]{article}

\usepackage{setspace}
\doublespacing

\usepackage{natbib}
\bibliographystyle{apalike}

\usepackage[margin=1.0in]{geometry}

\usepackage{amsmath}

\usepackage{lineno}

\usepackage{graphicx}
\linenumbers

%opening
\title{Predicting detection probabilities for rare and undersampled North American landbirds}
%\author{
%	Edwards, Brandon P.M.\\
%	\and
%	Gahbauer, Marcel A.\\
%	\and
%	Grinde, Alexis\\
%	\and
%	Hope, David\\
%	\and
%	Knight, Elly C.\\
%	\and
%	Michel, Nicole L.\\
%	\and
%	Robinson, Barry G.\\
%	\and
%	Solymos, Peter\\
%	\and
%	Bennett, Joseph R.\\
%	\and
%	Smith, Adam C.\\
%}
\date{}
\begin{document}

\maketitle

\begin{abstract}

@@

\end{abstract}

@@

\bibliography{refs}

@@

\begin{figure}[h]
	\includegraphics{../output/plots/1vs1.png}
	\caption{1-to-1 plot comparing cue rates (A) and EDRs (B) estimated from the single-species model vs the multi-species model for each species. Red dashed line denotes the 1-to-1 line. Black line is regression line with posterior draws in grey. Grey dots are individual species.}
	\label{fig:1vs1}
\end{figure}

\begin{figure}[h]
	\includegraphics{../output/plots/sd_comp.png}
	\caption{LOESS curves of standard deviations of cue rate (A) and EDR (B) for species modelled by a single-species model (blue lines) and multi-species model (red lines).}
	\label{fig:sd}
\end{figure}

\begin{figure}[h]
	\includegraphics{../output/plots/parameters_plot.png}
	\caption{Group parameter posterior distributions for multi-species removal model (A) and multi-species distance model (B).}
	\label{fig:params}
\end{figure}

\begin{figure}[h]
	\includegraphics{../output/plots/kfold_cv_plot.png}
	\caption{Mean difference in pointwise posterior predictive density for cue rate (A) and EDR (B) vs. log species sample size. Points are mean difference by species. Difference was calculated as multi-species minus single-species, and so positive differences (coloured in red for clarity) represent a multi-species model preference, whereas negative differences (coloured in blue for clarity) represent a single-species model preference. Grey points denote no differences. }
	\label{fig:cv}
\end{figure}

\begin{figure}[h]
	\includegraphics{../output/plots/species_cv_plot.png}
	\caption{(A) Estimates of cue rate for a species (black dots) given full data versus predictions of cue rate for the same species given no data. (B) Estimates of effective detection radius (EDR) for a species (black dots) given full data versus predictions of EDR for the same species given no data. For both, red dashed line denotes the 1-to-1 line. Black line is regression line with posterior draws in grey.}
	\label{fig:species_cv}
\end{figure}

\begin{figure}[h]
	\includegraphics{../output/plots/species_cv_distance_traits.png}
	\caption{Estimates of effective detection radius (EDR) for a species (dots) given full data versus predictions of EDR for the same species given no data, focusing in on species with EDRs between 60 m and 150 m. Colours denote discrete trait group combinations of migratory strategy and habitat preference. Red dashed line denotes the 1-to-1 line. Black line is regression line with posterior draws in grey.}
	\label{fig:distance_cv_traits}
\end{figure}

\begin{figure}[h]
	\includegraphics{../output/plots/predictions_figure.png}
	\caption{(A) Cue rates (red circles) and 90\% credible interval (red lines) for seven species of rare and undersampled North American landbirds. Species are 4 letter banding codes: LEPC = Lesser Prairie-chicken (n = 45), SPOW = Spotted Owl (n = 7), BITH = Bicknell's Thrush (n = 0), LCTH = LeConte's Thrasher (n = 1), HASP = Harris's Sparrow (n = 65), TRBL = Tricoloured Blackbird (n = 74), and KIWA = Kirtland's Warbler (n = 0). Black points are cue rate estimates of other similar species with the same migration strategy, with the opacity of the point indicating the strength of the relationship. (B) Effective detection radius (red circles) and 90\% credible interval (red line) for six species of rare and undersampled North American landbirds. Species are 4 letter banding codes: LEPC = Lesser Prairie-chicken (n = 45), SPOW = Spotted Owl (n = 28), BITH = Bicknell's Thrush (n = 0), LCTH = LeConte's Thrasher (n = 1), HASP = Harris's Sparrow (n = 13), KIWA = Kirtland's Warbler (n = 1). Black points are EDR estimates of species with the same migration strategy and habitat preference, and with a mass and pitch within 40\% in either direction.}
	\label{fig:predictions}
\end{figure}

>>>>

\chapter{Predicting detection probabilities for rare and undersampled North American landbirds}

\section{abstract}

@@

@@

@@

\begin{figure}[h]
	\includegraphics{../ch4-multispecies-detectability/output/plots/1vs1.png}
	\caption{1-to-1 plot comparing cue rates (A) and EDRs (B) estimated from the single-species model vs the multi-species model for each species. Red dashed line denotes the 1-to-1 line. Black line is regression line with posterior draws in grey. Grey dots are individual species.}
	\label{fig:1vs1}
\end{figure}

\begin{figure}[h]
	\includegraphics{../ch4-multispecies-detectability/output/plots/sd_comp.png}
	\caption{LOESS curves of standard deviations of cue rate (A) and EDR (B) for species modelled by a single-species model (blue lines) and multi-species model (red lines).}
	\label{fig:sd}
\end{figure}

\begin{figure}[h]
	\includegraphics{../ch4-multispecies-detectability/output/plots/parameters_plot.png}
	\caption{Group parameter posterior distributions for multi-species removal model (A) and multi-species distance model (B).}
	\label{fig:params}
\end{figure}

\begin{figure}[h]
	\includegraphics{../ch4-multispecies-detectability/output/plots/kfold_cv_plot.png}
	\caption{Mean difference in pointwise posterior predictive density for cue rate (A) and EDR (B) vs. log species sample size. Points are mean difference by species. Difference was calculated as multi-species minus single-species, and so positive differences (coloured in red for clarity) represent a multi-species model preference, whereas negative differences (coloured in blue for clarity) represent a single-species model preference. Grey points denote no differences. }
	\label{fig:cv}
\end{figure}

\begin{figure}[h]
	\includegraphics{../ch4-multispecies-detectability/output/plots/species_cv_plot.png}
	\caption{(A) Estimates of cue rate for a species (black dots) given full data versus predictions of cue rate for the same species given no data. (B) Estimates of effective detection radius (EDR) for a species (black dots) given full data versus predictions of EDR for the same species given no data. For both, red dashed line denotes the 1-to-1 line. Black line is regression line with posterior draws in grey.}
	\label{fig:species_cv}
\end{figure}

\begin{figure}[h]
	\includegraphics{../ch4-multispecies-detectability/output/plots/species_cv_distance_traits.png}
	\caption{Estimates of effective detection radius (EDR) for a species (dots) given full data versus predictions of EDR for the same species given no data, focusing in on species with EDRs between 60 m and 150 m. Colours denote discrete trait group combinations of migratory strategy and habitat preference. Red dashed line denotes the 1-to-1 line. Black line is regression line with posterior draws in grey.}
	\label{fig:distance_cv_traits}
\end{figure}

\begin{figure}[h]
	\includegraphics{../ch4-multispecies-detectability/output/plots/predictions_figure.png}
	\caption{(A) Cue rates (red circles) and 90\% credible interval (red lines) for seven species of rare and undersampled North American landbirds. Species are 4 letter banding codes: LEPC = Lesser Prairie-chicken (n = 45), SPOW = Spotted Owl (n = 7), BITH = Bicknell's Thrush (n = 0), LCTH = LeConte's Thrasher (n = 1), HASP = Harris's Sparrow (n = 65), TRBL = Tricoloured Blackbird (n = 74), and KIWA = Kirtland's Warbler (n = 0). Black points are cue rate estimates of other similar species with the same migration strategy, with the opacity of the point indicating the strength of the relationship. (B) Effective detection radius (red circles) and 90\% credible interval (red line) for six species of rare and undersampled North American landbirds. Species are 4 letter banding codes: LEPC = Lesser Prairie-chicken (n = 45), SPOW = Spotted Owl (n = 28), BITH = Bicknell's Thrush (n = 0), LCTH = LeConte's Thrasher (n = 1), HASP = Harris's Sparrow (n = 13), KIWA = Kirtland's Warbler (n = 1). Black points are EDR estimates of species with the same migration strategy and habitat preference, and with a mass and pitch within 40\% in either direction.}
	\label{fig:predictions}
\end{figure}
